Deep Probabilistic Models for Camera Geo-Calibration

### 2018-07-27 chapters/introduction/introduction.tex
minor changes

  \item \textbf{Constraint for Coarse Geographic Locations:}
  In this work, we demonstrate to estimate the camera geographic
  location with the input image.
  We provide two approaches to obtain the probability distribution over the camera
  geographic location. Most straightforwardly, our network output
  categorical distribution over world into a $N \times M$ bins. Better
  results can be obtained with temporal inputs (image timestamps). Other
  than that, our algorithm can also compute the probability for any
  geographic location.
  We present the algorithm details in \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and estimating the camera geo-orientation.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to methods that driven by
  the projective losses \todo{citation}, our network learns 
  both the geometric projection between the overhead and ground
  images, and the semantics of the overhead images jointly. 
  When refining the camera geographic location, we compare the
  semantic layout of the ground image with those transferred from
  overhead images sampled from different locations and orientations. The
  optimal prediction is found when the semantic layouts from these
  two sources fit best. For probabilistic outputs, we can also assign
  an energy score to each location and orientation combination
  according to how well the semantic layouts match to each other.
  We present the algorithm details in \chapref{crosstransf}
  \newline

>>>>

  \item \textbf{Constraint for Coarse Geographic Locations:}
  In this work, we demonstrate to estimate the camera geographic
  location with the input image.
  We provide two approaches to obtain the probability distribution over the camera
  geographic location. Most straightforwardly, our network outputs
  categorical distribution over world into a $N \times M$ bins. Better
  results can be obtained with temporal inputs (image timestamps).
  Our algorithm can also compute the probability at arbitrary
  geographic location, with lower accuracy than the straightforward
  method.
  We also demonstrate that our algorithm can learn a  geo-temporal
  feature representation of image with geographic locations and capture
  time.
  We present the algorithm details in \chapref{whenwhere}.
  \newline

  \item \textbf{Constraint for Fine Geographic Locations and Orientations}
  In our previous method, we present that our algorithm can estimate
  the camera location distribution in low-res world division. In this
  work we focus on refining the geo-localization results with the help
  of overhead imagery and on estimating the camera geo-orientation.
  Current machine learning methods address problems that involves mostly
  the ground imagery. Tons of dataset targeting on ground imagery are
  annotated while much fewer are done for the overhead imagery.
  In this work, we try to transfer the semantics from the ground imagery
  to the overhead imagery by identifying the latent geometry
  correspondences between these two. Similar to the monocular depth
  estimation methods that driven by
  the technique called {\em Reprojection
  Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}, our
  network learns to geometrically project pixels from the overhead
  images to the ground images,
  and learns to segment the overhead images jointly. 
  When refining the camera geographic location, we compare the
  semantic layout of the ground image with those transferred from
  overhead images sampled from different locations and orientations. The
  optimal prediction is found when the semantic layouts from these
  two sources match best. For probabilistic outputs, we can also assign
  an energy score to each location and orientation combination
  according to how well the semantic layouts match to each other.
  We present the algorithm details in \chapref{crosstransf}
  \newline
